---
title: "Electric Vehicle Project"
author: "Clement Cheng"
date: "2022-12-08"
output:
  pdf_document: default
  html_document: default
---


This is a project related to Electric Vehicle. In this project, I am using the "ElectricCarData_Clean.csv" to solve 5 questions by the author for practicing my skills in R.

Data Source: Kaggle "EVs - One Electric Vehicle Dataset - Smaller" by GEOFF839

Last updated: 12/8/2022


Let's install and load packages!

```{r}
install.packages("tidyverse") 
install.packages("sqldf")
install.packages("ggplot2")

library("tidyverse") # Basic package for data analysis
library("sqldf") # Find one off answers
library("ggplot2") # For visualization
```

Set the data frame and preview the file

```{r}
df <- read.csv("/cloud/project/ElectricCarData_Clean.csv")
head(df)
```

Let's see if the data frame has missing value or duplicates

```{r}
is.na(df)

duplicated(df)
```

It seems the data is clean for processing

Start the Analysis! Solving Q1: Which car has the fastest 0-100 acceleration? My thoughts: Sort the data by [AccelSec]

```{r}
sort(df$AccelSec) # Using sort the find the lowest Accel Sec
sqldf("SELECT Brand, Model, AccelSec FROM df WHERE AccelSec = 2.1") # Using sqldf to find the details of electric vehicle has AccelSec as 2.1
```

A1: Tesla's Roadster has the fastest 0-100 acceleration as 2.1.

Solving Q2: Which has the highest efficiency? My thoughts: Sort the data by [Efficiency_WhKm]

```{r}
sort(df$Efficiency_WhKm, decreasing = TRUE)
sqldf("SELECT Brand, Model, Efficiency_WhKm From df WHERE Efficiency_WhKm = 273")# Using sqldf to find the details of electric vehicle has Efficiency_WhKm as 273
```

A2: Mercedes's EQV 300 Long has the highest efficiency as 273 WhKm.

Solving Q3: Does a difference in power train effect the range, top speed, efficiency? My thoughts: Using ggplot to show the distribution between power train and range, power train and speed, and power train and efficiency.

```{r}
ggplot(df, aes(PowerTrain, Range_Km))+geom_boxplot()+labs(title = "Difference Between Different PowerTrain and Range", x="PowerTrain Type", y="Range_Km") # plots for showing the difference between power train and range
```

EV's with AWD PowerTrain are the best performer in Range, then FWD, last RWD. It was determined by the minimum range Km the electric vehicle can drove.

```{r}
ggplot(df, aes(PowerTrain, TopSpeed_KmH))+geom_boxplot()+labs(title = "Difference Between Different PowerTrain and TopSpeed_KmH", x="PowerTrain Type", y="TopSpeed_KmH") # plots for showing the difference between power train and top speed
```

EV's with AWD PowerTrain are the best performer in Top Speed, then RWD, last FWD. It was determined by the minimum top speed Km per hour.

```{r}
ggplot(df, aes(PowerTrain, Efficiency_WhKm))+geom_boxplot()+labs(title = "Difference Between Different PowerTrain and Efficiency_WhKm", x="PowerTrain Type", y="Efficiency_WhKm") # plots for showing the difference between power train and efficiency 
```

EV's with AWD PowerTrain are the best performer in Efficiency, then RWD, last FWD. It was determined by the average efficiency_WhKm.

A3: Overall, EV's with AWD PowerTrain will have better performance in range, speed, and efficiency.

Solving Q4: Which Manufacturer has the most number of vehicles? My thoughts: Using sqldf for counting vehicles in each brand

```{r}
sqldf("SELECT DISTINCT Brand, COUNT(Brand) as num_vehicels FROM df GROUP BY Brand")
```

A4: Tesla has the most number of vehicles.

Solving Q5: How does price related to rapid charging My thoughts: Using ggplot to show the distribution between price and rapid charging

```{r}
ggplot(df, aes(RapidCharge, PriceEuro))+geom_boxplot()+labs(title = "Difference Between Different PowerTrain and Price", x="Rapid Charge", y="Price in Euro") # plots for showing the difference between power train and efficiency 
```

A5: EVs that cost less than 50000 euro has low chance of equip with Rapid charge function, therefore, it means price and rapid charge function has a positive correlation.

That's the end of all questions. Thanks you for reading my project in R.
